### 2024-12-11 paper-en.tex
Add more literature

@@

\begin{theorem} \label{glued_paths}
    Let $G$ be a metagraph, $\mu = (e_1, \dots, e_d)$ and $\eta = (u_1, \dots, u_k)$ be paths on $G$ and let $\xi = (e_1, \dots, e_d, u_1, \dots, u_k)$ also be a path on $G$; let $\mu' = (e_d, \dots, e_1)$ be an inversion path of $\mu$. Then the following relations are true:

@@

\begin{proof}
    % Посмотреть, как по книжке Сосинского правильно описывать индукцию
    Conduct the proof by method of mathematical induction on the length of the path $|\eta| = d$.

@@

\begin{itemize}
    \item Add starting label $(a, 0, 0, nil)$ to an empty set of all labels,
    \item Iterating by $l$ from $1$ to $g / 2$:
    \begin{itemize}
        \item For all labels $(v, l - 1, ch, p)$:
        \item
            For each edge $e \not= p$ incident to vertex $v$,
            build label $(v', l, ch', p)$, where $ch' = ch + (-1)^{l} w(p)$, $v'$ is a vertex different from $v$, incident to $p$.
            Add this label to the set of all labels.
    \end{itemize}
    \item for all pairs of labels $(v_1, l_1, ch_1, p_1)$ and $(v_2, l_2, ch_2, p_2)$ such that $v_1 = v_2$ and $l_1 = l_2$, add inequality $ch_1 \neq \ch_2$ to the system $\mathcal{S}$.
\end{itemize}

@@

\begin{notice}
    Let us sequentially apply Algorithm 1 to $G$ with target girths of $4, 6, \dots, 2n$, where $2n$ is the first number for which algorithm couldn't build a solution. Then girth of metagraph $G$ is $2n - 2$.
\end{notice}

@@

Note that to construct graph with great girth metagraph with small girths should not be used. For example parallel edges must be avoided because they cause cycles with length $2$ significantly limiting the girth of an r-extension.

@@

% Список литературы: 15 штук

>>>>

\begin{notice}
    Sometimes the distinction between walks, trails and paths is made, in this paper we decided to use word path for all such objects.
\end{notice}

@@

\begin{theorem} \label{glued_paths}
    Let $G$ be a metagraph, $\mu = (e_1, \dots, e_d)$ and $\eta = (u_1, \dots, u_k)$ be paths on $G$ and let gluing $\xi = (e_1, \dots, e_d, u_1, \dots, u_k)$ also be a path on $G$; let $\mu' = (e_d, \dots, e_1)$ be an inversion path of $\mu$. Then the following relations are true:

@@

\begin{proof}
    % Посмотреть, как в Discrete math Ерусалимского Скороходова
    Conduct the proof by method of mathematical induction on the length of the path $|\eta| = d$.

@@

\begin{itemize}
    \item Add starting label $(a, 0, 0, nil)$ to an empty set of all labels,
    \item Iterating by $l$ from $1$ to $g / 2$:
    \begin{itemize}
        \item For all labels $(v, l - 1, ch, p)$:
        \item
            % Что-то тут не чисто с p
            For each edge $e \not= p$ incident to vertex $v$,
            build label $(v', l, ch', p)$, where $ch' = ch + (-1)^{l} w(p)$, $v'$ is a vertex different from $v$, incident to $p$.
            Add this label to the set of all labels.
    \end{itemize}
    \item for all pairs of labels $(v_1, l_1, ch_1, p_1)$ and $(v_2, l_2, ch_2, p_2)$ such that $v_1 = v_2$ and $l_1 = l_2$, add inequality $ch_1 \neq \ch_2$ to the system $\mathcal{S}$.
\end{itemize}

@@

% Какое-то странное замечание
\begin{notice}
    Let us sequentially apply Algorithm 1 to $G$ with target girths of $4, 6, \dots, 2n$, where $2n$ is the first number for which algorithm couldn't build a solution. Then girth of metagraph $G$ is $2n - 2$.
\end{notice}

@@

Note that to construct graph with great girth metagraph with small girths should not be used. For example parallel edges must be avoided because they cause cycles with length $2$ significantly limiting the girth of an r-expansion.

@@

\section{Conclusion.}

% Посмотреть какие времена используются в заключениях в других статьях
% Проверить, подходит ли слово precise в этом контексте

In this article we have proposed a structural method for construction of bipartite graphs with any given girth by expanding metagraphs. The algorithm for selection of optimal weights for metagraphs was developed. Precise estimation of girth among all expansions of metagraph was given. Algorithm for iterative selection of metragraph structure was proposed.

These algorithms and theorems might in future be generalized for any graphs. Generalized algorithms can be used for construction of structured graphs with specific properties.

\section{Literature.}

% Список литературы: ~15 штук

\bibitem{zemor}
G. Zémor, On Expander Codes, IEEE Trans. on Information theory, IT-47
No 2, (2001) pp. 835–837.

\bibitem{johnson}
S.\,J. Johnson,
Introducing Low-Density Parity-Check Codes.
~-- University of Newcastle, Australia, 2006.

\bibitem{gallager}
R.\,G. Gallager,
Low-density parity-check codes
~-- IRE Transactions on Information Theory, 1962.

\bibitem{protographs}
J. Thorpe,
Low-density parity-check (LDPC) codes constructed from protographs.
~-- JPL, IPN Progress Rep., Aug. 2003, vol. 42–154.

\bibitem{skorohodov_reachability_problem}
Skorokhodov V.A. Generalization of the Reachability Problem on Directed Graphs
~-- Mathematics and Statistics, Vol. 8, No. 6, pp. 699 - 704, 2020. DOI: 10.13189/ms.2020.080610

% \bibitem{metagraphs_and_applications}
% A. Basu, R.W. Blanning. Mategraphs and Their Applications
% ~-- %https://books.google.rs/books?id=9DlhUIJklqUC&printsec=frontcover#v=onepage&q&f=false

\bibitem{tutte_graph_definition}
W.T. Tutte, Graph Theory
~-- % https://books.google.rs/books?id=uTGhooU37h4C&printsec=frontcover#v=onepage&q&f=false
Chapter 1, page 1

%% https://errorcorrectionzoo.org/

%% G. A. MARGULIS EXPLICIT CONSTRUCTIONS OF GRAPHS WITHOUT SHORT CYCLES AND LOW DENSITY CODES 
%% https://sci-hub.se/10.1007/bf02579283

%% Imrich, W. (1984). Explicit construction of regular graphs without small cycles
%% https://sci-hub.se/10.1007/bf02579157

%% David J.C. MacKay, Michael S. Postol, Weaknesses of Margulis and Ramanujan–Margulis Low-Density Parity-Check Codes
%% https://www.inference.org.uk/mackay/margulis.pdf
%% Критика метода Маргулиса
